CLT Results

### 2022-04-06 analysis/clt_irt_analysis.Rmd
prep for unidimtest

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))

@@

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 5000), SE = T)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)

>>>>

# dimensionality
firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))

@@

library(psych)

unidim(firt_dat)

firt1 <- mirt(firt_dat, 1, itemtype = "Rasch",  guess = .25)
firt2 <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000), SE = T)
firt3 <- mirt(firt_dat, 1, itemtype = "3PL",  guess = .25)
